\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-13 paper/background.tex
remove dup background sections

Refraction networking fundamentally operates by injecting covert communication inside a client's HTTPS connection with a reachable site, also known as a decoy site. In a regular HTTPS session, a client establishes a TCP connection, performs a TLS connection with a destination site, sends an encrypted web request, and receives an encrypted response. In refraction routing, at least one direction of this exchange is observed by a \emph{refraction station} (RS), deployed at some Internet service provider (ISP). The RS watches for a covert signal from the client that this connection is to be used for censorship circumvention. Upon seeing the signal, the RS will take over the HTTPS session at some point, and establish a proxy session with the client that can then be used for covert communication.

>>>>

Refraction networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In refraction routing, at least one direction
of this exchange is observed by a \emph{refraction station} (RS), deployed at
some Internet service provider (ISP). The RS watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the RS will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.
